The State of Debugging for RxJS\\``Debugging of RxJS-Based Applications''

### 2020-11-16 slides.tex
Practice Talk Feedback

\note[itemize] {
    \item Welcome
    \item I am Manuel
    \item Master Student, OST, Switzerland
    \item I want to tell you a short story...
    \item State of debugging for RxJS
    \item You might think, well:
    \item ``It has JS in its name''
    \item JavaScript and Engineering?
}

@@

\note[itemize] {
    \item Thats frontend stuff!
    \item Are ``Frontend Engineers'' Engineers?
    \item Because of things like RxJS...
    \item Frontend Engineering came a long way!
    \item RxJS is RP with JavaScript
    \item Nice: TypeScript Interface
    \item Nice: RxJS is core part of Googles Angular
    \item Nice: Describe data flows
    \item Wait? Sales pitch?
    \item I have a story of frustration to tell: Debugging
}

@@

\note[itemize] {
    \item Back when i started with RP
    \item Debug? Ha! Breakpoint!
    \item Helped sometimes (lambda functions, ...)
    \item Often felt lost though
    \item Stack traces
    \item program step controls: Operator? No: Internals!
    \item What else?
}

@@

\note[itemize] {
    \item Especially when stuff gets complicated
    \item Debugging === Trace Logs
    \item Sprinkle log statements
    \item Analyze flood of logs
    \item Find problem
    \item Remove log states
    \item DONT remove the bug fix ;)
    \item This left me...
}

@@

\note[itemize] {
    \item Frustrated!
    \item Mature Software Engineer has to feel different
    \item Looked for existing solutions
    \item Good concepts for other languages (Scala)
    \item RxJS less stuff
    \item Lets do this on our own!
    \item -> Started with research questions
}

@@

\note[itemize] {
    \item Recruiting via Twitter and Email
    \item Personal Network
    \item 10 participants
    \item Daily users of RP
    \item One RxJS Core team member
    \item Two Google Dev Experts on Angular
}

\begin{frame}[fragile]{Five One-to-One Interviews}
	\begin{vfilleditems}
		\item How do you \textbf{use} Reactive Programming?
		\item Which aspects do you \textbf{like} on Reactive Programming?
		\item Which do you \textbf{dislike}?
	\end{vfilleditems}
\end{frame}

\note[itemize] {
    \item Interviews had no focus on debugging yet
    \item Interested in experience with RP
    \item Pros
    \item Cons
    \item Pain Points
}

\begin{frame}[fragile]{Five Written War Story Reports}
	\begin{vfilleditems}
		\item When did you \textbf{last} have to debug an RxJS-based Application?
		\item Do you remember a specific \textbf{challenging} debugging situation?
		\item How did you \textbf{solve} it? (If at all?)
	\end{vfilleditems}
\end{frame}

\note[itemize] {
    \item This time: Focused on debugging
    \item Hear about specific situations
    \item They should recall particular scenario
    \item Step by step
    \item What problems did they face tool?
    \item How did they overcome them?
}

@@

\note[itemize] {
    \item Improve the dev user experience
    \item Lower the boundary to use the right tool
    \item At the right time
    \item Integrate the right tools where they are expected the most
    \item Example: Async Stack Traces in Google Chrome
    \item Dont look for it: Its there where it belongs.
    \item Hence, outlook to future work...
}

@@

% \appendix
% \begin{frame}[allowframebreaks]{References}
% 	\printbibliography
% \end{frame}

>>>>

\note[itemize] {
    \item Welcome
    \item I am Manuel
    \item Frontend Engineer for 7 years
    \item Web and native mobile
    \item Now: Senior Frontend Engineer, Swiss Fintech
    \item Now: Master Student, OST, Switzerland
    \item In my talk about: State of debugging for RxJS
    \item I want to tell a story
}

@@

\note[itemize] {
    \item JS, frontend, frontend engineer...
    \item Are ``Frontend Engineers'' Engineers?
    \item Because of things like RxJS...
    \item Frontend Engineering came a long way!
    \item RxJS is RP with JavaScript
    \item Nice: TypeScript Interface
    \item Nice: RxJS is core part of Googles Angular
    \item Nice: Describe data flows
    \item Wait? Sales pitch?
    \item I have another story:
    \item About: Debugging
}

@@

\note[itemize] {
    \item Back when i started with RP
    \item Debug? Ha! Breakpoint!
    \item Helped sometimes (lambda functions, ...)
}

\begin{frame}[fragile]{Debugging: First Intuition}
    \begin{figure}[H]
        \centering
        \includegraphics[height=\textheight/2]{figures/stacktrace.png}
        \caption{Stack Trace}
    \end{figure}
\end{frame}

\note[itemize] {
    \item Often felt lost though
    \item Stack traces
    \item program step controls: Operator? No: Internals!
    \item What else is possible?
}

@@

\note[itemize] {
    \item Especially when stuff gets complicated
    \item Debugging === Trace Logs
    \item Sprinkle log statements
}

\begin{frame}[fragile]{Debugging: The Reality}
    \begin{figure}[H]
        \centering
        \includegraphics[height=\textheight/2]{figures/tracelogs.png}
        \caption{Flood of Trace Logs}
    \end{figure}
\end{frame}

\note[itemize] {
    \item Analyze flood of logs
    \item Find problem
    \item Remove log states
    \item DONT remove the bug fix ;)
    \item This left me...
}

@@

\note[itemize] {
    \item Frustrated!
    \item Mature Software Engineer has to feel different
    \item Looked for existing solutions
}

\begin{frame}[fragile]{A New Hope?}
    \begin{vfilleditems}
        \item \textbf{Reactive Inspector} for REScala \cite{10.1145/2577080.2577083}, Salvaneschi et al. \cite{10.1145/2884781.2884815} \cite{10.1145/2889160.2893174}
        \item \textbf{RxFiddle}, Banken et al. \cite{10.1145/3180155.3180156}
        \item Better trace logs using \textbf{rxjs-spy} \cite{rxjsspy}
    \end{vfilleditems}
\end{frame}

\note[itemize] {
    \item Own research
    \item Some interesting findings
    \item Most elaborate: Reactive Inspector
    \item Salvaneschi et al
    \item REScala, Scala
    \item Some, but not a lot for RxJS
    \item rxfiddle, banken et al -> Visualizer Externally
    \item rxjs-spy: Better logs, but still: trace log approach
    \item MEH!
    \item Lets do this on our own!
    \item -> Started with research questions
}

@@

\note[itemize] {
    \item Recruiting via Twitter and Email
    \item 10 participants
    \item Daily users of RP
    \item One RxJS Core team member
    \item Two Google Dev Experts on Angular
}

\begin{frame}[fragile]{Scope}
    \begin{columns}[T]
        \begin{column}{.4\linewidth}

            \begin{vfilleditems}
                \item Five \textbf{Interviews}\vspace{1em}
                \item General \textbf{Experience} with Reactive Programming\vspace{0.5em}
                \item What do you \textbf{like}?\vspace{0.5em}
                \item What do you \textbf{dislike}?
        	\end{vfilleditems}
        \end{column}
        \begin{column}{.4\linewidth}
            \begin{vfilleditems}
                \item Five War Story \textbf{Reports}\vspace{1em}
        		\item Recall a specific \textbf{challenging} debugging situation?\vspace{0.5em}
        		\item How did you \textbf{solve} it?
        	\end{vfilleditems}
        \end{column}
    \end{columns}
\end{frame}

\note[itemize] {
    \item Experience with RP
    \item Pros
    \item Cons / Pain Points
    \item They should recall particular scenario
    \item Step by step
    \item What problems?
    \item How did they solve them?
}

@@

\note[itemize] {
    \item Improve the dev user experience
    \item Lower the boundary to use the right tool
    \item At the right time
    \item Integrate the right tools where they are expected the most
    \item Dont look for it: Its there where it belongs.
    \item Hence, outlook to future work...
}

@@

\appendix
\begin{frame}[allowframebreaks]{References}
	\printbibliography
\end{frame}

\begin{frame}[plain, noframenumbering]{}
    \centering
    \vfill
    {\fontsize{30}{40}\selectfont\color{white}{Backup Slides}}
    \vfill
\end{frame}
